---
title: "Google Analytics - Analysis"
author: "Flávio Brito"
date: "15 de julho de 2016"
output: 
  html_document: 
    theme: cerulean
    toc: yes
---
DATA: **`r format(Sys.time(), "%d de %B de %Y")`**  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
load("~/Trabalho_OneDrive/OneDrive/Source/Repos/hulahulaga/hulahulaga.RData")
library(ggplot2)
library(lubridate)
library(xtable)

```

## Google Analytics - Analysis

This document shows deep analysis about Servidor Portal behaviour 

```{r df.Sessions.Date, echo=FALSE, warning=FALSE}

#Analysis
data <- df.Sessions.Date
```
###Texto
```{r echo=FALSE, warning=FALSE}
#Sessions
total.Sessions <- sum(data$sessions)
total_sessions <- prettyNum(total.Sessions, big.mark = ".", decimal.mark = ",")

#Users
total.Users <- sum(data$users)
total_users <- prettyNum(total.Users, big.mark = ".", decimal.mark = ",")

#Pageviews
total.Pageviews <- sum(data$pageviews)
total_pageviews <- prettyNum(total.Pageviews, big.mark = ".", decimal.mark = ",")

page_views <- prettyNum(total.Pageviews, big.mark = ".", decimal.mark = ",")


#Pages per Sessions
pages.per.Session <- sum(data$pageviews)/sum(data$sessions)
pages_per_Session <- prettyNum(pages.per.Session, big.mark = ".", decimal.mark = ",")


#Bouce Rate = ga:bounces / ga:sessions
bounce.Rate <- sum(data$bounces)/sum(data$sessions)
bounce_Rate <- prettyNum(bounce.Rate, big.mark = ".", decimal.mark = ",")

#Sessions AVG
sessions.avg <- mean(data$sessions)
sessions_avg <- prettyNum(sessions.avg , big.mark = ".", decimal.mark = ",")



````
<b>Total Sessions:</b>      `r  total_sessions` </br>
<b>Total Users:</b>         `r  total_users` </br>
<b>Pages Views:</b>         `r  page_views`</br>
<b>Pages per Sessions:</b>  `r  pages_per_Session`</br>
<b>Bouce Rate:</b>          `r  bounce_Rate`</br>
<b>Sessions AVG:</b>        `r  sessions_avg`</br>



```{r echo=FALSE, warning=FALSE}


data1 <- data
#It´ll be done bellow
analysis_Session_Date <- as.data.frame(xtabs(sessions ~ month(date) , data=data1))
````



###Crosstab - Sessions vs Date

```{r xtable, results="asis"}
#Print Crosstab
##Tabulation - Sessions vs Date
print(xtable(analysis_Session_Date), type="html", include.rownames = TRUE)
```


### Plot Sessions Series
```{r echo=FALSE, warning=FALSE}

ggplot(data,aes(x=date,y=sessions)) + geom_line()
```

### Bloxplot comparing Sessions by Year
```{r echo=FALSE, warning=FALSE}
library(lubridate)
year.vector <- year(data$date)
date_facts <- factor(year.vector)
boxplot(data=data,sessions~date_facts)

```

### Sessions by Month
```{r echo=FALSE, warning=FALSE}

#Line plot
ggplot(data,aes(x=date,y=sessions), breaks = date_breaks("month")) + geom_line()
```

### Plot Sessions Series with Adjusted Line
```{r echo=FALSE, warning=FALSE}

#Adjusted Plot
ggplot(data,aes(x=date,y=sessions)) +
  geom_point(alpha=0.5) +
  geom_smooth()


#Histogram
ggplot(data,aes(x=sessions)) + geom_histogram()

#Line Plot - Minimal Theme
ggplot(data,aes(x=date,y=sessions)) +
  geom_line() +
  theme_minimal()



ggplot(data,aes(x=date,y=sessions)) +
  geom_line() +
  geom_hline(yintercept=avg, size=5, color="red") +
  theme_minimal()

#Sessions per day over two years
ggplot(data,aes(x=date,y=sessions)) +
  geom_line() +
  geom_smooth() +
  theme_minimal() +
  xlab("Date") +
  ylab("Number of sessions") +
  ggtitle("Sessions per day over two years") +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        plot.title = element_text(size = 25))


#Sessions Scatter plot by Year
ggplot(data, aes(x=date,y=sessions, size=sessions, color=as.factor(year.vector))) +
  geom_point(alpha=0.8) +
  xlab("Year") +
  ylab("Sessions") +
  ggtitle("Sessions per day over two years") +
  scale_color_discrete(guide = guide_legend(title = "Year")) +
  scale_size_continuous(guide = guide_legend(title = "Sessions (Count)")) +
  theme_minimal() 


#Sessions Scatter plot by Year
ggplot(data, aes(x=date,y=sessions, size=sessions, color=as.factor(year.vector))) +
  geom_point(alpha=0.9) +
  xlab("Year") +
  ylab("Sessions") +
  ggtitle("Sessions per day over two years") +
  scale_color_discrete(guide = guide_legend(title = "Year")) +
  scale_size_continuous(guide = guide_legend(title = "Sessions (Count)"))

#Forecast Sessions
library(forecast)
sessionsts <- ts(data$sessions, frequency=7)
comp <- decompose(sessionsts)
plot(comp)
forecastmodel <- HoltWinters(sessionsts)
plot(forecastmodel)

sessionforecast <- forecast.HoltWinters(forecastmodel, h=30) # 30 days in future
plot(sessionforecast)

```


